% references.tex - 参考文献

\begin{thebibliography}{99}

\bibitem{chsims}
Yu, W., Xu, H., Meng, F., Zhu, Y., Ma, Y., Wu, J., Jiang, J., and Yang, S.
\textit{CH-SIMS: A Chinese Multimodal Sentiment Analysis Dataset with Fine-grained Annotations of Modality}.
Proceedings of the 58th Annual Meeting of the Association for Computational Linguistics (ACL), 2020, pp. 3718--3727.

\bibitem{bert}
Devlin, J., Chang, M. W., Lee, K., and Toutanova, K.
\textit{BERT: Pre-training of Deep Bidirectional Transformers for Language Understanding}.
Proceedings of the 2019 Conference of the North American Chapter of the Association for Computational Linguistics (NAACL), 2019, pp. 4171--4186.

\bibitem{resnet}
He, K., Zhang, X., Ren, S., and Sun, J.
\textit{Deep Residual Learning for Image Recognition}.
Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2016, pp. 770--778.

\bibitem{opensmile}
Eyben, F., Wöllmer, M., and Schuller, B.
\textit{openSMILE: The Munich Versatile and Fast Open-Source Audio Feature Extractor}.
Proceedings of the 18th ACM International Conference on Multimedia (MM), 2010, pp. 1459--1462.

\bibitem{mtcnn}
Zhang, K., Zhang, Z., Li, Z., and Qiao, Y.
\textit{Joint Face Detection and Alignment Using Multitask Cascaded Convolutional Networks}.
IEEE Signal Processing Letters, 2016, 23(10): 1499--1503.

\bibitem{poria_survey}
Poria, S., Cambria, E., Bajpai, R., and Hussain, A.
\textit{A Review of Affective Computing: From Unimodal Analysis to Multimodal Fusion}.
Information Fusion, 2017, 37: 98--125.

\bibitem{zadeh_mosi}
Zadeh, A., Zellers, R., Pincus, E., and Morency, L. P.
\textit{MOSI: Multimodal Corpus of Sentiment Intensity and Subjectivity Analysis in Online Opinion Videos}.
IEEE Intelligent Systems, 2016, 31(6): 82--88.

\bibitem{transformer}
Vaswani, A., Shazeer, N., Parmar, N., Uszkoreit, J., Jones, L., Gomez, A. N., Kaiser, Ł., and Polosukhin, I.
\textit{Attention Is All You Need}.
Advances in Neural Information Processing Systems (NeurIPS), 2017, pp. 5998--6008.

\end{thebibliography}
